\documentclass[]{usiinfbachelorproject}

\usepackage{float}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{chngcntr}
\usepackage{xcolor}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

\counterwithin{figure}{section}

\captionsetup{labelfont={bf}}

\author{Andrea Vicari}
\newcommand{\applicationName}{Smart--IVC}
\newcommand{\cfbox}[2]{%
    \colorlet{currentcolor}{.}%
    {\color{#1}%
    \fbox{\color{currentcolor}#2}}%
}
\title{\applicationName}
\subtitle{Enhanced Visualization of Cities Through Smart Visual Queries}
\versiondate{\today}
\begin{committee}
%With more than 1 advisor an error is raised...: only 1 advisor is allowed!
\advisor[Universit\`a della Svizzera Italiana, Switzerland]{Prof.}{Michele}{Lanza}
%You can comment out  these lines if you don't have any assistant
\assistant[Universit\`a della Svizzera Italiana, Switzerland]{Dr.}{Andrea}{Mocci}
\end{committee}


\abstract {Cities constantly evolve, with the appearance of new neighborhoods and the disappearance of old buildings. Information about cities are nowadays stored as static data inside huge storages where it is difficult and slow to retrieve particular information. Moreover, different data sources about cities are not aggregated since they are provided by both public websites on the Internet and by public sectors of the city.\\

A visualization can help supporting any decision that involves city evolution,  especially in the contest of what is called a Smart City. No such service exists that provides a unique environment in which the user can both visualize a city and interact with its elements. The only technologies available are either not exhaustive or too complex to use. For example, it is possible to find technologies online that are limited to provide a 3D--visualization without any kind of interaction between the map and the user.\\

\applicationName\ provides an interactive 3D--visualization  model of cities,  integrating heterogeneous data, and supporting complex visual queries. \applicationName\ is  an application accessible by everyone (since it is both user--friendly and publicly available) and that aims to enhance the city visualization, getting closer to the user needs.

%Web users have to aggregate different data from various sources whenever they are looking for some information on the Internet. Think about the student who is looking for a rented room near her university: she firstly uses a specific website to find the advertisement of a room for rent, she then looks for the address on another website that provides a map service to see if the house is located where she desires.\\
%
%No such service exists that provides a unique environment in which the user can both visualize a city and interact with its elements. The only technologies available are either not exhaustive or too complex to use.\\
%
%This thesis introduces \applicationName\ a web application that provides an intuitive interface and prevents the user from jumping from website to website. Through the form of a 3D-environment, this application provides an interactive visualisation of cities in which the user can directly “communicate” with the elements, executing queries on them. After having clicked on a building in the map, the user is able to get information (coordinates, address, floors etc.) about that construction and also find out what are the various relations between that specific building and the other entities in the city.\\
}

\begin{document}
\maketitle
\thispagestyle{empty}
\tableofcontents
\newpage
\thispagestyle{empty}
\listoffigures
%\listoftables
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%
\include{introduction/introduction_content}
%%%%%%%%%%%%%%%%%%%%%%%%%
\include{chapter2/chapter2_content}
%%%%%%%%%%%%%%%%%%%%%%%%%
\include{chapter3/chapter3_content}
%%%%%%%%%%%%%%%%%%%%%%%%%
\include{chapter4/chapter4_content}
%%%%%%%%%%%%%%%%%%%%%%%%%
\include{chapter5/chapter5_content}
%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{table}[h]
%\centering
%\scalebox {0.8} {
%\begin{normalsize}\begin{tabular}{l|lll}
%\textbf{Col 1} & \textbf{Col 2} & \textbf{Col 3} & \textbf{Col 4}\\
%\hline
%1 & 2 & 3 & Goofy\\
%4 & 5 & 6 & Mickey
%\end{tabular}
%\end{normalsize}
%}
%\caption{Caption of the table}
%\label{tab:numbers}
%\end{table}

%\cite{Stru1899a}
%%%%%
%\newpage
%\bibliographystyle{abbrv}
%\bibliography{references}

\end{document}