\documentclass[]{usiinfbachelorproject}

\captionsetup{labelfont={bf}}

\author{Andrea Vicari}

\title{Smart Interactive Visualisation of Cities}
\subtitle{Cities becoming alive}
\versiondate{\today}

\begin{committee}
%With more than 1 advisor an error is raised...: only 1 advisor is allowed!
\advisor[Universit\`a della Svizzera Italiana, Switzerland]{Prof.}{Michele}{Lanza}
%You can comment out  these lines if you don't have any assistant
\assistant[Universit\`a della Svizzera Italiana, Switzerland]{Dr.}{Andrea}{Mocci}
\end{committee}

\abstract {
Web users have to aggregate different data from various sources whenever they are looking for some information on the internet.  Just think of the student who is looking for a rented room near his university: he uses a website to find an advertisement and then he looks for the address on another website to see if the house is near the university or near some facility.

The aim of this Bachelor Project is to create a Web Application that prevents the user from jumping from website to website. It will provide an interactive visualisation of cities in the form of a 3D-environment in which the user can directly communicate with elements in the city, executing queries on them. After having clicked on a building in the map, the user will be able to get information (coordinates, address, floors etc.) about that construction and even find out what is the nearest public place.

Therefore, this is an application accessible by everyone that aims to enhance the city visualisation getting closer to the user needs.

}


\begin{document}
\maketitle
\end{document}